WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-04 introduction/sec_2-problem_and_objectives.tex
Thesis 4.0
v5.1
After Dilum sir fixes

\section{Objectives}
This research addresses the above problem statement by achieving the following research objectives:
\begin{itemize}
    \item To develop an open platform to integrate weather data from different sources in different formats
    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage
    \item To optimize schema to support data queries based on geography and time
    \item To develop an API for third-party data sharing
%    \item To use open source tools and provide the source publicly with appropriate liecense.
\end{itemize}

>>>>

\section{Objectives}
This research addresses the above problem statement by achieving the following research objectives:
\begin{itemize}
    \item To develop a platform to integrate weather data from different sources in different formats
    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage
    \item To optimize data schema to support geospatial and time-based queries
    \item To develop an API for third-party data sharing
\dbc{Add a another objective for performance analysis}
%    \item To use open source tools and provide the source publicly with appropriate liecense.
\end{itemize}

### 2020-05-04 summary/sec_1-conclusions.tex
v5.1
After Dilum sir fixes

During our research, we proposed an extendable open source weather data integration and assimilation system known as \acrshort{wdias}. \acrshort{wdias} focuses on providing a system to efficiently integrate weather data from different sources with quality control and supporting steaming large size of data. Furthermore, the proposed system is compatible with current cloud computing technologies, architecture patterns, and compatible with modern cloud computing architectures.

First, the architecture of \acrshort{wdias} starts with \acrshort{soa} using an \acrfull{esb} and then moved to Actor model-based architecture. After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture. \acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}, which is a container orchestration platform. We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster. Also, each microservice follows the concept of smart endpoints dumb pipes[?] and does specific operations that are related to the data format that responsible for handling.

Based on the microservice architecture patterns and the nature of the weather metadata, we came up with the idea of database structure for the \acrshort{wdias} to provide higher performance while storing the weather data optimum. The system uses a timeseries database for storing scalar and vector timeseries data and using netCDF for storing grid timeseries data. Also, each database has an adapter, and each adapter uses the concept of database per service, which allows each microservice service to scale without getting interference from other microservices.
Moreover, it uses the microservice sagas pattern for asynchronous data handling for requests with a larger size. As discussed in \cref{se:microservice}, we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

@@

Further, we performed load tests using the JMeter tool’s distributed testing capabilities. Then the test plans are performed with increasing the request size and monitoring the performance metrics. The system is setup on the Amazon Elastic Kubernetes Service (Amazon EKS) as per the system setup configurations of \cref{subse:test_sys_config}. Based on the observations, we were able to perform 300 \acrshort{rps} of peak load, and the system handled the workload successfully with minimizing the error rate to zero. Also, while we increased the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to provide the same throughput while keeping the latency constant without any significant change. Likewise, the system was able to provide an increase in the throughput by keeping the latency constant while increasing the workload. Thus, we can conclude that the system is further scalable.
With \acrshort{k8s} auto-scaling enabled, the \acrshort{k8s} elastically adjust the number of pods according to the workload with provided auto-scaling configurations. The results of \acrshort{wdias} shows that the system can run on a cluster from 1 CPU node to nodes with a few hundred CPUs.

>>>>

In this research, we proposed an extendable weather data integration and assimilation system known as \acrfull{wdias}. \acrshort{wdias} focuses on providing a system to efficiently integrate weather data from different sources with quality control and supporting steaming large size of data. Furthermore, the proposed system is compatible with current cloud computing technologies, architecture patterns, and compatible with modern cloud computing architectures.

First, the architecture of \acrshort{wdias} starts with \acrshort{soa} using an \acrfull{esb} and then moved to actor model-based architecture. After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture. \acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}, which is a container orchestration platform. We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster. Also, each microservice follows the concept of smart endpoints dumb pipes[?] and does specific operations that are related to the data format that responsible for handling.
\dbc{Need to explain the solution based on microservices as it's the most important. Also, a reference is missing here}

Based on the microservice architecture patterns and the nature of the weather metadata, we designed database structure of \acrshort{wdias} to provide higher performance while storing the weather data efficiently. The system uses a timeseries database for storing scalar and vector timeseries data and using netCDF for storing grid timeseries data. Also, each database has an adapter, and each adapter uses the concept of database per service, which allows each microservice service to scale without getting interference from other microservices.
Moreover, it uses the microservice sagas pattern for asynchronous data handling for requests with a larger size. As discussed in \cref{se:microservice}, we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

@@

%Further, we performed load tests using the JMeter tool’s distributed testing capabilities. Then the test plans are performed with increasing the request size and monitoring the performance metrics. 
We evaluated the performance using a cloud-based setup on the Amazon Elastic Kubernetes Service (Amazon EKS). % as per the system setup configurations of \cref{subse:test_sys_config}. 
Based on the performance analysis, we were able to perform 300 \acrshort{rps}, and the system handled the workload successfully with minimizing the error rate. Also, while we increased the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to provide the same throughput while keeping the latency constant. Likewise, the system was able to provide an increase in the throughput by keeping the latency constant while increasing the workload. Thus, we can conclude that the system is scalable. With \acrshort{k8s} auto-scaling enabled, the \acrshort{k8s} elastically adjust the number of pods according to the workload with provided auto-scaling configurations. The results of \acrshort{wdias} shows that the system can run on a cluster from 1 CPU node to nodes with a few hundred CPUs.
